### 2014-06-12 src/paper1/results.tex
Fixed some references

    \caption{SBT versus SVV performance in one subject (S1). Top, SBT. Proportion of CW responses is plotted against body orientation relative to the reference orientation (0\textdegree, \textpm45\textdegree, or \textpm90\textdegree). $\mu > 0\degree$ indicates tilt underestimation. Bottom, SVV. Proportion of CW responses is plotted against line orientation relative to vertical. Solid lines, Best-fit cumulative Gaussians, typified by $\mu$ and $\sigma$.}  
\end{figure}

@@

    \caption{Model predictions superimposed on parameters from the psychometric fits to the SBT (two top rows) and SVV data (two bottom rows). Accuracy and variability characteristics as a function of roll-tilt angle are shown; values are psychometric fits ($\mu$ and $\sigma$ values, [CIRCLES]) and model predictions (line) from all subjects. Mean data and mean predictions across subjects are plotted in the rightmost column.}
\end{figure}

@@

The bold lines in Figure 4 present the predictions of the Bayesian integration model, fitted simultaneously to the original responses from the SBT and SVV tasks. The rightmost column of Figure 4 shows the mean predictions from this model superimposed on the averaged parameters from the psychometric fits, indicating that the sensory integration model can account very well for all the characteristics of the data.

@@

For each subject, best-fit parameter values and their bootstrap-based SD levels are listed in Table 1. Parameter bHS, representing the noise (sHS) in the otolith signal in the upright subject, ranges between 1.1∞ and 3.9∞. Best-fit values of parameter aHS are significantly positive (p < 0.05) for all subjects, ranging from 0.07∞/∞ (S4) to 0.23∞/∞ (S1). This implies that the noise in the otoliths increases with tilt angle. The width of the head-in-space prior (sHSP) ranges from 9.4∞ (S2) to 18.7∞ (S5), with a mean of 12.5 ± 3.2∞, consistent with our previous report \cite{devrijer2009}. Best-fit values of parameter sBS, reflecting the noise in the sensory body-in-space signal, range from 6.7∞ (S3) to 15.0∞ (S5), with a mean of 10.8 ± 3.1∞, which is about twice as large as the best-fit values of parameter sHB, reflecting noise in the head-on-body signal, ranging from 1.8∞ (S6) to 9.3∞ (S3), with a mean of 4.9 ± 2.7∞. Thus, the parameter fits imply that the neck sensors are more precise than the body-tilt sensors. As has been discussed extensively in our previous paper \cite{devrijer2009}, the amplitude of uncompensated ocular counterroll (AOCR) shows large intersubject variability.

@@

\caption{Best-fit parameter and bootstrap-based SD values}
\end{table}

@@

To obtain the model fits in Figure 4, we made the assumption (see Introduction) that information from both direct and indirect pathways (Fig. 1) is used to estimate body and head orientation in space. The sensory weights, indicating the relative contribution of both pathways, can be computed from the fit results in Table 1. To obtain the body-in-space estimate, necessary for the SBT, the model uses both direct information from the body sensors and indirect information from the combination of otolith and neck information. Because the variability of the otolith signal (sHS) increases with tilt angle (aHS > 0), as shown in Table 1, the relative importance of direct and indirect pathways becomes dependent on tilt angle. This can be seen in Figure 5(top row), which shows the relative weights of these signals for each subject, derived from Equation 2 and the best-fit parameter values in Table 1. The mean (±SD) pattern across subjects is shown in the rightmost pattern.

@@

\begin{table}
\begin{tabular}{llllll}
\hline
Subject & MLE full model & MLE reduced model & $p$ & BIC full model & BIC psychometric fits \\
\hline
S1 & 231.5 & 312.4 & SMALLERTHAN 0.001 & 498.1 & 540.3 \\
S2 & 197.8 & 216.9 & SMALLERTHAN 0.001 & 430.6 & 539.3 \\
S3 & 267.5 & 313.4 & SMALLERTHAN 0.001 & 570.0 & 548.2 \\
S4 & 207.5 & 218.2 & SMALLERTHAN 0.001 & 450.0 & 569.1 \\
S5 & 195.6 & 216.3 & SMALLERTHAN 0.001 & 426.2 & 571.0 \\
S6 & 163.5 & 183.2 & SMALLERTHAN 0.001 & 362.0 & 502.5 \\
S7 & 248.0 & 260.0 & SMALLERTHAN 0.001 & 531.1 & 633.5 \\ 
\hline
\multicolumn{6}{l}{Log-likelihood ratio test of the full model (with indirect pathways) and reduced model (without indirect pathways). For all subjects, the full model outperforms the reduced model lacking multisensory integration through the indirect pathways. BIC values are much lower for the Bayesian integration model compared with separate psychometric fits in six of seven subjects.} \\
\end{tabular}
\caption{Validation of the model}
\end{table}

We also compared our model, which provides a mechanistic explanation of the full dataset, with the pure descriptive account of the data as obtained by fitting separate psychometric curves to the data for the five SBT angles and nine SVV angles (Eq. 1, Fig. 3, and Materials and Materials and Methods, Model evaluation). Maximum-likelihood estimates were calculated and corrected for the number of free parameters using the BIC. As shown in Table 2, we found the lowest BIC values, indicating a better model, for the Bayesian model in all subjects, except S3. One might argue that the mean corrections before fitting the Bayesian model added another nine parameters that should be taken into account when comparing the models, even though these parameters were not fitted by the model. However, even for the worst-case scenario of 16 parameters, our Bayesian model still outperformed the individual psychometric fits (BICmechanistic = 3583 < BICpsychometric = 3910).

@@

To further validate the model, we independently tested one of its predictions that can be assessed experimentally in isolation: head-on-body variance. In supine position, subjects judged their head orientation (CW/CCW) relative to the body midline after it had been passively roll-rotated with speeds subthreshold for the canals to various angles (see Materials and Methods, Model validation: independent test of neck noise). Psychometric fits indicate no systematic bias in these head-on-body percepts (data not shown). Figure 6 depicts the experimental noise levels derived from these psychometric fits and the predicted values provided by the model, including their 95\% confidence intervals. Because the variance of the estimates increases with the average head-on-body percept, we performed a regression on the log-transformed data \cite{hopkins2000}. The significant correlation between predicted and measured neck noise levels (slope, 1.03; intercept, -0.1; p = 0.04) provides an independent confirmation of the proposed model.

>>>>

    \caption{SBT versus SVV performance in one subject (S1). Top, SBT. Proportion of CW responses is plotted against body orientation relative to the reference orientation (0\textdegree, \textpm45\textdegree, or \textpm90\textdegree). $\mu > 0\degree$ indicates tilt underestimation. Bottom, SVV. Proportion of CW responses is plotted against line orientation relative to vertical. Solid lines, Best-fit cumulative Gaussians, typified by $\mu$ and $\sigma$.}  
    \label{p1:fig3}
\end{figure}

@@

    \caption{Model predictions superimposed on parameters from the psychometric fits to the SBT (two top rows) and SVV data (two bottom rows). Accuracy and variability characteristics as a function of roll-tilt angle are shown; values are psychometric fits ($\mu$ and $\sigma$ values, [CIRCLES]) and model predictions (line) from all subjects. Mean data and mean predictions across subjects are plotted in the rightmost column.}
    \label{p1:fig4}
\end{figure}

@@

The bold lines in Figure \ref{p1:fig4} present the predictions of the Bayesian integration model, fitted simultaneously to the original responses from the SBT and SVV tasks. The rightmost column of Figure \ref{p1:fig4} shows the mean predictions from this model superimposed on the averaged parameters from the psychometric fits, indicating that the sensory integration model can account very well for all the characteristics of the data.

@@

For each subject, best-fit parameter values and their bootstrap-based SD levels are listed in Table \ref{p1:tab1}. Parameter bHS, representing the noise (sHS) in the otolith signal in the upright subject, ranges between 1.1∞ and 3.9∞. Best-fit values of parameter aHS are significantly positive (p < 0.05) for all subjects, ranging from 0.07∞/∞ (S4) to 0.23∞/∞ (S1). This implies that the noise in the otoliths increases with tilt angle. The width of the head-in-space prior (sHSP) ranges from 9.4∞ (S2) to 18.7∞ (S5), with a mean of 12.5 ± 3.2∞, consistent with our previous report \cite{devrijer2009}. Best-fit values of parameter sBS, reflecting the noise in the sensory body-in-space signal, range from 6.7∞ (S3) to 15.0∞ (S5), with a mean of 10.8 ± 3.1∞, which is about twice as large as the best-fit values of parameter sHB, reflecting noise in the head-on-body signal, ranging from 1.8∞ (S6) to 9.3∞ (S3), with a mean of 4.9 ± 2.7∞. Thus, the parameter fits imply that the neck sensors are more precise than the body-tilt sensors. As has been discussed extensively in our previous paper \cite{devrijer2009}, the amplitude of uncompensated ocular counterroll (AOCR) shows large intersubject variability.

@@

\caption{Best-fit parameter and bootstrap-based SD values}
\label{p1:tab1}
\end{table}

@@

To obtain the model fits in Figure \ref{p1:fig4}, we made the assumption (see Introduction) that information from both direct and indirect pathways (Fig. \ref{p1:fig1}) is used to estimate body and head orientation in space. The sensory weights, indicating the relative contribution of both pathways, can be computed from the fit results in Table 1. To obtain the body-in-space estimate, necessary for the SBT, the model uses both direct information from the body sensors and indirect information from the combination of otolith and neck information. Because the variability of the otolith signal (sHS) increases with tilt angle (aHS > 0), as shown in Table 1, the relative importance of direct and indirect pathways becomes dependent on tilt angle. This can be seen in Figure 5(top row), which shows the relative weights of these signals for each subject, derived from Equation 2 and the best-fit parameter values in Table 1. The mean (±SD) pattern across subjects is shown in the rightmost pattern.

@@

\begin{table}
\begin{tabular}{llllll}
\hline
Subject & MLE full model & MLE reduced model & $p$ & BIC full model & BIC psychometric fits \\
\hline
S1 & 231.5 & 312.4 & \textless 0.001 & 498.1 & 540.3 \\
S2 & 197.8 & 216.9 & \textless 0.001 & 430.6 & 539.3 \\
S3 & 267.5 & 313.4 & \textless 0.001 & 570.0 & 548.2 \\
S4 & 207.5 & 218.2 & \textless 0.001 & 450.0 & 569.1 \\
S5 & 195.6 & 216.3 & \textless 0.001 & 426.2 & 571.0 \\
S6 & 163.5 & 183.2 & \textless 0.001 & 362.0 & 502.5 \\
S7 & 248.0 & 260.0 & \textless 0.001 & 531.1 & 633.5 \\ 
\hline
\multicolumn{6}{l}{Log-likelihood ratio test of the full model (with indirect pathways) and reduced model (without indirect pathways). For all subjects, the full model outperforms the reduced model lacking multisensory integration through the indirect pathways. BIC values are much lower for the Bayesian integration model compared with separate psychometric fits in six of seven subjects.} \\
\end{tabular}
\caption{Validation of the model}
\label{p1:tab2}
\end{table}

We also compared our model, which provides a mechanistic explanation of the full dataset, with the pure descriptive account of the data as obtained by fitting separate psychometric curves to the data for the five SBT angles and nine SVV angles (Eq. \ref{p1:eqn1}, Fig. \ref{p1:fig3}, and \nameref{p1:sec:methods}, Model evaluation). Maximum-likelihood estimates were calculated and corrected for the number of free parameters using the BIC. As shown in Table 2, we found the lowest BIC values, indicating a better model, for the Bayesian model in all subjects, except S3. One might argue that the mean corrections before fitting the Bayesian model added another nine parameters that should be taken into account when comparing the models, even though these parameters were not fitted by the model. However, even for the worst-case scenario of 16 parameters, our Bayesian model still outperformed the individual psychometric fits (BICmechanistic = 3583 < BICpsychometric = 3910).

@@

To further validate the model, we independently tested one of its predictions that can be assessed experimentally in isolation: head-on-body variance. In supine position, subjects judged their head orientation (CW/CCW) relative to the body midline after it had been passively roll-rotated with speeds subthreshold for the canals to various angles (see \nameref{sec:methods}, Model validation: independent test of neck noise). Psychometric fits indicate no systematic bias in these head-on-body percepts (data not shown). Figure 6 depicts the experimental noise levels derived from these psychometric fits and the predicted values provided by the model, including their 95\% confidence intervals. Because the variance of the estimates increases with the average head-on-body percept, we performed a regression on the log-transformed data \cite{hopkins2000}. The significant correlation between predicted and measured neck noise levels (slope, 1.03; intercept, -0.1; p = 0.04) provides an independent confirmation of the proposed model.
